Top Text

### 2022-12-06 Paper.tex
c

The best text-to-image generator out of the four we chose will be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image) which allows the user more freedom to fine-tune their result. Given enough time this will yield a more accurate result.

@@

	This paper is used as an attempt to prove that stable diffusion is the best application out of the four, we chose. Our x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications. The intervening variable in this case would be experience using these applications.

	We have chosen an image that we find sufficiently covers all the hard parts of recreating an image using ai art generation such as reflections and complex composition. We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (30 minutes ) and after each iteration we take that image and compile it into a list of the iterations for the process of recreating that image for that specific application. With those sets of data, we then plug the images (each iteration) into an AI application that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate. this then gives us insight into how fast the application is (how efficient its technique is) and how many iterations you have to do to achieve a certain result. Once the data is gathered, we can create a graph to compare the applications more easily. The people that carried out this experiment also consisted of one novice and one experienced individual. This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs. In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of them use we can notice if there is a pattern of success or failure with each.

	\section{Results}
	\newpage	
	\section{Discussion}

>>>>

The best text-to-image generator out of the four we chose will be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image) which, this allo user more freedom to fine-tune their result. Given enough time this will yield a more accurate result. This however, only applies for artists who are already experienced, we expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get. In the case of inexperienced artists, they might find DallE easier to use because it creates photo realistic results without having to fine tune any settings apart from their prompt.

@@

	This paper is used as an attempt to prove that stable diffusion is the best application out of the four, we chose. Our x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications. The intervening variable in this case would be the amount of experience using these applications.

	We have chosen an image that we find sufficiently covers all the challenging parts of recreating an image using ai art generation such as reflections and complex composition. We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes). After each iteration we take the generated image (iteration) and add it to a list of the iterations that we created while recreating that image for that specific application(each application will thus have their own history of the process of the participants tying to recreate the image). With those sets of data, we then plug the images (each iteration) into an AI application that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate. this then gives us insight into how fast the application is (how efficient its technique is) and how many iterations you have to do to achieve a certain result. Once the data is gathered, we can create a graph to compare the applications more easily. The people that carried out this experiment also consisted of one novice and one experienced individual. This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs(one graph for each group of people). In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of the ai generation applications use, we can notice if there is a pattern of success or failure with each and thus are able to compare them and see which one is the best.

	In order to compare the image generation applications effectively we observe a multitude of factors that will indicate the strengths and weaknesses of that application. These fators are: The amount of iterations each participant can generate while trying to create the image within the 15 minute time limit, how close each iteration is to the image we are trying to replicate using the ai image comparing program's unit of measurement (the unit is called distance. The closer to zero the distance is, the closer the images are together. zero means that the two images that are being compared are exactly the same), how easily we were able to access the application and its functionality, how much functionality each application offers and their effects on the final results of our experiment.

	\section{Results}

	\newpage
    \begin{figure}
    	\centering
    	\includegraphics[width=1\linewidth]{Bargraph}
    	\caption{}
    	\label{fig:bargraph}
    \end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=1\linewidth]{LineGraphStableDiff}
		\caption{}
		\label{fig:linegraphstablediff}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=1\linewidth]{LineGraphDall-E}
		\caption{}
		\label{fig:linegraphdall-e}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=1\linewidth]{LineGraphDBW}
		\caption{}
		\label{fig:linegraphdbw}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=1\linewidth]{LineGraphMidJ}
		\caption{}
		\label{fig:linegraphmidj}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=1\linewidth]{boxplotWithAllData}
		\caption{}
		\label{fig:boxplotwithalldata}
	\end{figure}

	\section{Discussion}
